HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ddd

\subsection{One vs. Two Structures}

\subsection{Verbal Structures Only?}

\subsection{Monolingual vs. Bilingual Evaluation}
+/- expects to cover the whole hypothesis with annotations, whereas HMEANT 'gives up' when the
hypothesis is not intelligible, giving a zero score to the bad frame/whole sentence.
This can be a good decision for HMEANT, since our way may artificially boost the chances of
understanding the sentence.

\subsection{Technical Differences}

+ allows for multi-word and even non-contiguous elements

+ allows to indicate the quality of the predicates ("Actions")

\subsection{XXX to be moved}

@@

\subsection{from e-mails}

@@

>>>>

@@

@@

\subsection{Copied from emails}

+ allows for multi-word and even non-contiguous elements
+ allows to indicate the quality of the predicates ("Actions")
+/- expects to cover the whole hypothesis with annotations, whereas HMEANT 'gives up' when the
hypothesis is not intelligible, giving a zero score to the bad frame/whole sentence.
This can be a good decision for HMEANT, since our way may artificially boost the chances of
understanding the sentence.

HMEAN disadvantages:
. Importantly: it disregards copula clauses, nominalizations (which are often translated to verbal clauses), inter-clause relations (discourse markers, complement clauses etc.). UCCA-Eval addresses these.
